TacticToe: Learning the Game of Tactics

### 2018-02-13 tactictoe_jv.tex
Fix warninig

\subsection{Similarity}\label{sec:predictions}
We estimate the similarity (or co-distance) between two objects $o_1$ and $o_2$
through their respective feature sets $f_1$ and $f_2$.
%The similarity function $sim$ computed by the k-NN algorithm is analogous
%to the one used in the premise selection task~\cite{ckju-pxtp13}.
The estimation is based on the frequency of the features in the intersection of
$f_1$ and $f_2$. A good rule of thumb is that the rarer the shared features
are, the more similar two goals should be. The relative rarity of each feature
can be estimated by calculating its TF-IDF weight~\cite{Jones72astatistical}.
We additionally modify the weight by raising them to the sixth power giving
even more credence
to rare features which was found experimentally optimal in \cite{}.\todo{CK:
citation}

@@

Thanks to the larger search time available in this experiment, the timeout for
each tactic can be raised from the 0.02 seconds used in \tactictoe's first
experiment~\cite{lpar} to 0.05
seconds. Removing tactics with similar effect as performed by the
orthogonalization process is only beneficial when running \tactictoe for short
period of time. It seems that the alloted time allows a strategy
running without orthogonalization to catch up.
It is best to predict a list of 16 theorems to instantiate arguments of type
theorem list in tactics. At any rate, argument prediction for abstracted
tactics is the technique that have the highest impact on the success of
\tactictoe. Integration of ATPs being a specialization of this technique
contributes significantly as well. Experiments involving \eprover, run the ATP
on one thread asynchronously with a timeout of 5 seconds and 128 premises.
The fact that \metis outperforms \eprover in this setting is due to the fact
that \metis is run with a very short timeout, allowing to close different part
of search tree quickly. Because \metis is weaker that \tactictoe as an ATP, it
is given less predictions. But even if a lemma essential for the proof of a
goal is not predicted, a modification on the goal performed by a tactic can
change its prediction to include the necessary lemma.
This effect minimizes the drawback of relying on a small number of predictions.

>>>>

\subsection{Similarity}\label{sec:predictions}
We estimate the similarity (or co-distance) between two objects $o_1$ and $o_2$
through their respective feature sets $f_1$ and $f_2$.
%The similarity function $sim$ computed by the k-NN algorithm is analogous
%to the one used in the premise selection task~\cite{ckju-pxtp13}.
The estimation is based on the frequency of the features in the intersection of
$f_1$ and $f_2$. A good rule of thumb is that the rarer the shared features
are, the more similar two goals should be. The relative rarity of each feature
can be estimated by calculating its TF-IDF weight~\cite{Jones72astatistical}.
We additionally modify the weight by raising them to the sixth power giving
even more credence
to rare features which was found experimentally optimal in \cite{ckju-pxtp13}.

@@

Thanks to the larger search time available in this experiment, the timeout for
each tactic can be raised from the 0.02 seconds used in \tactictoe's first
experiment~\cite{tgckju-lpar17} to 0.05
seconds. Removing tactics with similar effect as performed by the
orthogonalization process is only beneficial when running \tactictoe for short
period of time. It seems that the alloted time allows a strategy
running without orthogonalization to catch up.
It is best to predict a list of 16 theorems to instantiate arguments of type
theorem list in tactics. At any rate, argument prediction for abstracted
tactics is the technique that have the highest impact on the success of
\tactictoe. Integration of ATPs being a specialization of this technique
contributes significantly as well. Experiments involving \eprover, run the ATP
on one thread asynchronously with a timeout of 5 seconds and 128 premises.
The fact that \metis outperforms \eprover in this setting is due to the fact
that \metis is run with a very short timeout, allowing to close different part
of search tree quickly. Because \metis is weaker that \tactictoe as an ATP, it
is given less predictions. But even if a lemma essential for the proof of a
goal is not predicted, a modification on the goal performed by a tactic can
change its prediction to include the necessary lemma.
This effect minimizes the drawback of relying on a small number of predictions.
